# Making a call to the Botometer API from R
output: html_document

Botometer [checks the activity of a Twitter account and gives it a score based on how likely the account is to be a bot. Higher scores are more bot-like.](https://botometer.iuni.iu.edu/#!/)

Using the [Botometer API](https://market.mashape.com/OSoMe/botometer) is pretty simple. You POST a .json file that [looks like the example request payload here](https://market.mashape.com/OSoMe/botometer) and then receive the response. [Read the overview](https://market.mashape.com/OSoMe/botometer/overview) for more information.

The API documentation provides example API requests in a variety of formats, but there aren't any examples using R. This very simple script is a template you can use for making calls to Botometer in R.

You must first [get your own API key](https://market.mashape.com/OSoMe/botometer). Then load libraries:

```{r, eval=FALSE}
library(httr)
library(xml2)
library(RCurl)
library(ROAuth)
library(rjson)
library(openssl)
library(httpuv)
```

Next, read in the example .json file included in this repo:

```{r, eval=FALSE}
testbody = upload_file("test.json")
```

Then POST the file to Botometer, replacing "XXXXX" with your key:

```{r, eval=FALSE}
result <- POST("https://osome-botometer.p.mashape.com/2/check_account",
               verbose(),
               encode="json",
               add_headers(`X-Mashape-Key`="xxxxxxxxxxxxxxx"),
               body=testbody)
```


And look at the results:

```{r, eval=FALSE}
content(result)
```


You should get a brief response that let's you know the test was successful. To post real Twitter data to the API, you'll need to collect tweets, maybe using [twitteR](https://www.rdocumentation.org/packages/twitteR/versions/1.1.9) or [streamR](https://cran.r-project.org/web/packages/streamR/index.html), construct a .json payload like the example one above, and POST it to Botometer.









